### 2020-06-29 introduction.tex
revision by cl

To mitigate this threat, massive efforts have been made, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}. All of these methods however require additional deployment cost \cite{Chun2019Keep} and cannot be widely deployed for critical privacy stages (e.g., password entry) of most scenarios. Furthermore, none of existing works can deal with the presence of developed smartphone cameras and SR algorithms in shoulder surfing scenarios. Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it's imminent to recall attention on this new privacy threat and propose the corresponding countermeasure for modern circumstances.

In this paper, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm. Deployed on commercial smartphones, it can take multiple snapshots of the target screen continuously and stealthily from a long range, illustrated in Figure~\ref{illustration_of_system}. Benefited from our multi-frame SR neural network, those blurred images can be then aligned, cropped, and processed, delivering a holistic threat model for acquisition of high-resolution contents of the victim.

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{pic/intro.png}
    \caption{Illustration of the long-range shoulder surfing threat model on smartphones, exacerbated by the SR algorithm. \cl{supplement elements for long range, blurred input and the recognized results.}}
	\label{illustration_of_system}
\end{figure}

@@

  \item \textbf{Model complexity and variable input.} We have to operate our threat model locally on comercial smartphones in a real-time manner rather than remotely in cloud server. Since 1) the latter would require stable Internet access, and 2) sending multiple images across the Internet will consume time and bandwith. Given the required 10 to 20 images to process for ideal contennt recovery, we have 1-2s as the minimum interval between each output frame, rendering limited period for calculation with restricted power and RAM. In cases where the display on the target screen changes more frequently, less images and processing time are avaliable for each scene. Consequently, it cannot only require a smaller and simpler network model, but also a model that can deal with dyanmic inputs efficiently, either 3 or 20 images.
  \item \textbf{Complexities of characters.} To make our threat model more applicable for real-life scenarios (e.g., passwords or e-mails), we aim for reconstructing multi-type texts, including Chinese characters, English letters, and numbers. And it poses unique challenges compared with scene or object reconstruction. Composed of multiple strokes, characters are distributed discretely in image space, not known to other entities, e.g. faces and natural objects. In some cases, messing up a stroke will not impact its readability, and in other cases shortening or lengthening a stroke even slightly will lead to a different character, leading to misunderstandings. And unlike most SR applications working on similarity (between their output and the ‘ground truth’), our goal is readability, and the network architecture and training process must be engineered accordingly.\cl{ Another challenge is imbalanced data. Among Chinese characters certain strokes and stroke groups are always more commonplace than others, and this imbalanceness often results in lower prediction accuracy over the less common,  unconventionality shaped characters. On the other hand, however, the focus on characters can also aid us. As our network is only expected to reconstructe these characters, the network can learn to detect features from the input and reconstruct strokes and segments from them, extracting more information from the blurry images.}

@@

\vspace{1mm}
\noindent
\textbf{Contributions.} This paper makes the following contributions:
\begin{itemize}[leftmargin=*]
  \item	We propose \textsf{SRPeek}, a multi-frame SR neural network architecture aiming at reconstructing extremely blurred and defocused images. This model is not only functional in our scenario, as a shoulder-surfing threat model, but also can be used in text-recognition applications prior to recognition algorithms to increase accuracy.
  \item	We design a threat model of shoulder-surfing, with the attacker armed with multi-frame SR algorithms and taking multiple photos (in burst mode) of the victim’s screen with a smartphone camera. To the best of our knowledge, we are the first to consider the presence of smartphone cameras and SR algorithms in shoulder surfing scenarios.
  \item	We demonstrate the effect of this shoulder-surfing attack and prove that it poses a threat to screen privacy.
\end{itemize}

% describe the organization of the paper
The rest of the paper is organized as follows. Section 2 describes the threat model of our  carefully studies the performance of state-of-the-art concurrent flooding. The detailed design of COFlood protocol is shown in Section~\ref{sec-design}. We show the implementation details and evaluation results in Section~\ref{sec-implementation-and-evaluation}. The related work is introduced in Section~\ref{sec-related-work}. Finally, we conclude our work in Section~\ref{sec-conclusion}.

>>>>

To mitigate this threat, massive efforts have been made, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}. All of these methods however require additional deployment cost \cite{Chun2019Keep} and cannot be widely deployed for critical privacy stages (e.g., password entry) of most scenarios. Furthermore, none of existing works can deal with the presence of developed smartphone cameras and SR algorithms in shoulder surfing scenarios. Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it's imminent to recall attention on this new privacy threat and propose the corresponding countermeasure for modern circumstances.
\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{pic/intro.png}
    \caption{Illustration of the long-range shoulder surfing threat model on smartphones, exacerbated by the SR algorithm. \cl{supplement elements for long range, blurred input and the recognized results.}}
	\label{illustration_of_system}
\end{figure}

\vspace{1mm}
\noindent
\textbf{Threat Model.} We present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm, illustrated in Figure~\ref{illustration_of_system}. 
Assuming the victim is scanning messages in life, the attacker can raise his commercial smartphone with powerful lenses and our SR network to the victim stealthily, even from a long range (e.g., 1.5 meters far away within the visual angle of 30$^{\circ}$). As the camera zooms in, he can take 20 to 30 snapshots continuously in burst mode, with about 0.05 ~ 0.1 seconds of interval between frames. This process can take about 2 seconds with the consistent content and position for the screen of the victim. Benefited from our multi-frame SR neural network, those blurred snapshots can be then aligned, cropped, and processed, delivering a holistic threat model for acquisition of high-resolution contents of the victim in real time. Note that multi-type contents can be recovered accurately on the smartphone screen of the victim, covering numbers, English and Chinese characters. The above procedure can be automated by an app and repeated every few seconds, giving the attacker a continuous surveillance over the victim’s screen.

@@

  \item \textbf{Model complexity and variable input.} We have to operate our threat model locally on commercial smartphones in a real-time manner rather than remotely in cloud server. Since 1) the latter would require stable Internet access, and 2) sending multiple images across the Internet will consume time and bandwidth. Given the required 10 to 20 images to process for ideal content recovery, we have 1-2s as the minimum interval between each output frame, rendering limited period for calculation with restricted power and RAM. In cases where the display on the target screen changes more frequently, less images and processing time are available for each scene. Consequently, it cannot only require a smaller and simpler network model, but also a model that can deal with dynamic inputs efficiently, either 3 or 20 images.
  \item \textbf{Complexities of characters.} To deploy our threat model broadly for real-life scenarios (e.g., record passwords or e-mails), it is supposed to reconstruct multi-type texts, including Chinese characters, English letters, and numbers. Composed of multiple strokes, characters are distributed discretely in the pixel-wise image and different with other entities (e.g., faces and natural objects), rendering unique challenges. In some cases, messing up a stroke even slightly can shorten or lengthen a stroke, leading to a different character for misunderstandings. Unlike most SR applications working on similarity between their output and the ground truth, our network architecture and training process must be engineered to recover readable contents. Another challenge is the imbalanced element for words. Since we know certain stroke or alphabet of Chinese and English characters can occur more frequently, results in lower prediction accuracy over the less common, unconventionality shaped characters.

@@

\vspace{1mm}
\noindent
\textbf{Contributions.} This paper makes the following contributions:
\begin{itemize}[leftmargin=*]
  \item	We propose \textsf{SRPeek}, an end-to-end threat model of shoulder surfing from a broad range. To the best of our knowledge, we are the first to consider the presence of smartphone cameras and SR algorithms in shoulder surfing scenarios.
  \item	We design a multi-frame SR neural network architecture aiming at reconstructing extremely massive blurred and defocused snapshots. It can be further extended to other text-recognition applications on commercial smartphones.
  \item	We evaluate this new shoulder surfing attack in comprehensive scenarios. And it outperforms the state-of-the-arts for the new privacy concern.
\end{itemize}
% describe the organization of the paper
The rest of the paper is organized as follows. Section~\ref{sec-related-work} describes the related work, especially the state-of-the-arts for the shoulder surfing attack. We present the system and network design in Section~\ref{sec-design}, followed by the implementation and evaluation in Section~\ref{sec-implementation-and-training} and~\ref{sec-evaluation}, respectively. We further wrap up this paper by presenting the limitations and countermeasures of our system in Section~\ref{sec-limitations-and-discussions}. And the conclusion is show in Section~\ref{sec-conclusion}.

### 2020-06-29 related_work.tex
revision by cl

\section{Related Work}
\label{sec-related-work}
\subsection{Shoulder Surfing}
With the arrival of the information era, privacy issues are becoming increasingly prominent. Smartphone screen privacy, the concern of our smartphones being observed by strangers in public areas, or shoulder surfing, have been studied heavily in recent years. Surveys of shoulder surfing provides evidence of this behavior in real world \cite{eiband2017understanding} \cite{goucher2011look}, often more efficient than expected\cite{kwon2013covert}. Various techniques and systems have been designed to mitigate this threat. Some systems sense malicious passers-by and hide information \cite{brudy2014anyone} or warn the user\cite{saad2018communicating}; others modify the user interfaces to create honeypots (for passwords)\cite{chakraborty2014tag}, confuse unauthorized parties\cite{wiedenbeck2006design}, or making the interactions invisible\cite{kumar2007reducing} or unreadable from a distance\cite{Chun2019Keep}. Most of the works designing defenses against shoulder surfing assume that the attacker is a casual passer-by, taking occasional peeks with his/hers naked eye, as is the case most of the time\cite{eiband2017understanding}. However, it is the malicious ones, although few, that can utilize the information (passwords, business correspondence, etc.) they obtained to do real harm. On the other hand, the threat model of tool-assisted shoulder surfing is also studied. Schaub, et, al. observed the susceptibility of shoulder surfing from the naked eye\cite{schaub2012password}. Maggi, et al. designed an automatic shoulder surfing threat model, observing the target smartphone with a camera\cite{maggi2011poster}, but without the help of SR techniques, this method can only function when the attacker is standing at close range, which is a barely practical scenario. With the development of smartphone camera, processing ability, and SR technology over the years, we propose a stronger shoulder surfing system in which attackers can successfully obtain information while keeping a distance to avoid suspicion, and prove that this threat is eminent in our daily life.

>>>>

\section{Related Work}
\label{sec-related-work}
\begin{table*}[t]
    \caption{A comparison of state-of-the-art works on Wi-Fi Imaging.}
    \vspace{2mm}
    \begin{center}
    \begin{tabular}{ccccc}
    \hline
     Reference  & Principle &  RF Platform & Method & \#(Tx,Rx) Ant$^{\mathrm{a}}$\\ 
    \hline
    Wision~\cite{wision}  & Intensity & USRP-N210 & SAR & (1,8$\times$8)\\ 
    RF\_Avatar~\cite{rf_avatar}  & Intensity & FMCW Radio & DNN & (4,16)\\ 
    C. Karanam~\cite{3dimaging_uav} & Intensity (RSSI) & COTS Wi-Fi & SAR & (1,150$\times$150)$^{\mathrm{c}}$\\ 
    P. Proffitt~\cite{imaging_1} & Intensity & USRP-N210 & SAR \& DNN~\cite{MaskRCNN} & (180, 180)$^{\mathrm{b}}$\\ 
    P. Holl~\cite{holography} & Intensity \& Phase & 3D Hologram Simulation & Wave Front~\cite{angular} & (1,50$\times$40)$^{\mathrm{d}}$\\ 
    \hline
    \textbf{\textsf{WiHolo-2D}} & Intensity \& Polarization & COTS Wi-Fi & 2D IFFT \& GAN &(1,6) \\
    \hline
    \multicolumn{5}{l}{$^{\mathrm{a}}$Equivalent static antenna array for antenna scanning. $^{\mathrm{b}} $The receive beam sweeps from $+90^{\circ}$ to $-90^{\circ}$ for one}\\
    \multicolumn{5}{l}{transmit beam angle between $+90^{\circ}$ and $-90^{\circ}$. $^{\mathrm{c}}$The RX drone measures the RSSI every 2 cm for the 3m$\times$3m area.}\\
    \multicolumn{5}{l}{$^{\mathrm{d}}$Achieve a resolution of 4.0 cm $\times$ 7.2 cm for the 2m$\times$3m area.}\\
    \end{tabular}
    \label{comparison}
    \end{center}
\end{table*}

\cl{Compare existing work from several views to present advanntages of SRPeek. Keep the related work part within the page 3.}
\subsection{Shoulder Surfing}
With the arrival of the information era, privacy issues are becoming increasingly prominent. Smartphone screen privacy, the concern of our smartphones being observed by strangers in public areas, or shoulder surfing, have been studied heavily in recent years. Surveys of shoulder surfing provides evidence of this behavior in real world \cite{eiband2017understanding} \cite{goucher2011look}, often more efficient than expected\cite{kwon2013covert}. Various techniques and systems have been designed to mitigate this threat. Some systems sense malicious passers-by and hide information \cite{brudy2014anyone} or warn the user\cite{saad2018communicating}; others modify the user interfaces to create honeypots (for passwords)\cite{chakraborty2014tag}, confuse unauthorized parties\cite{wiedenbeck2006design}, or making the interactions invisible\cite{kumar2007reducing} or unreadable from a distance\cite{Chun2019Keep}. Most of the works designing defenses against shoulder surfing assume that the attacker is a casual passer-by, taking occasional peeks with his/hers naked eye, as is the case most of the time\cite{eiband2017understanding}. However, it is the malicious ones, although few, that can utilize the information (passwords, business correspondence, etc.) they obtained to do real harm. On the other hand, the threat model of tool-assisted shoulder surfing is also studied. Schaub, et, al. observed the susceptibility of shoulder surfing from the naked eye\cite{schaub2012password}. Maggi, et al. designed an automatic shoulder surfing threat model, observing the target smartphone with a camera\cite{maggi2011poster}, but without the help of SR techniques, this method can only function when the attacker is standing at close range, which is a barely practical scenario. With the development of smartphone camera, processing ability, and SR technology over the years, we propose a stronger shoulder surfing system in which attackers can successfully obtain information while keeping a distance to avoid suspicion, and prove that this threat is eminent in our daily life.

### 2020-06-29 system_overview.tex
revision by cl

The outline of this network is as follows:

>>>>

To solve the challenges and outperform the state-of-the-arts for this new shoulder surfing attack, we propose a holistic system with the multi-frame SR neural network, illustrated in Figure~\ref{fig-workflow}.
\cl{These four parts are too long, try to whittle it away to half its length. Refer to the revised contents for challenges in Section introduction.}
